


---
  title: "Group Project_DDA"
author: "Group"
date: "`r Sys.Date()`"
output: html_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Step-2:Data Cleaning

```{r}
install.packages("dplyr")
install.packages("reshape2")
```

```{r}
library(tidyverse)
library(skimr)
library(validate)
library(ggplot2)
library(PerformanceAnalytics)
library(reshape2)
```


```{r}
Telco <- read.csv(file= 'C:/Users/Santosh/Downloads/Telco-Customer-Churn.csv')
```

```{r}
names(Telco)
```

```{r}
nrow(Telco)
ncol(Telco)
```
```{r}
summary(Telco)
```


```{r}
str(Telco)
```
```{r}
Telco%>%skim()
```
```{r}
boxplot(Telco$TotalCharges, xlab= "TotalCharges", main= "Boxplot of TotalCharges")
```



```{r}
table(Telco$gender)
```

```{r}
table(Telco$SeniorCitizen)
```

```{r}
table(Telco$Partner)
```

```{r}
table(Telco$Dependents)
```

```{r}
table(Telco$tenure)
```

```{r}
table(Telco$PhoneService)
```
```{r}
table(Telco$MultipleLines)
```
"Yes": indicates that the customer has multiple phone lines included in their subscription.
"No": indicates that the customer does not have multiple phone lines included in their subscription.
"No phone service": indicates that the customer does not have phone service at all and therefore does not have access to multiple phone lines.


```{r}
Telco_NA_count <- apply(is.na(Telco),2, sum)
Telco_NA_count
```
There are 11 NA's in Totalcharges column. And all the other columns are perfect and no NA's. 

# Lets clean the those 11 columns:

```{r}
Telco_cleandata <- na.omit(Telco)
```

```{r}
nrow(Telco)
nrow(Telco_cleandata)
```
Notice that, 11 rows removed. 

```{r}
Telco_cleandata%>%skim()
```

Check the thrid table, you will see no NA's 

Enjoy!!


### Step-3: Data Exploration

# visualize the distribution of numeric variables

```{r}
numeric_vars <- Telco_cleandata %>% select_if(is.numeric)
ggplot(melt(numeric_vars), aes(value)) + geom_histogram(binwidth = 5) + facet_wrap(~variable, scales = "free")
```
# Change the Yes/No to 1 and 0 respectively

```{r}
Telco_cleandata$Churn[Telco_cleandata$Churn == "Yes"] <- 1
Telco_cleandata$Churn[Telco_cleandata$Churn == "No"] <- 0
```


# PCA Test

```{r}
install.packages(stats)
install.packages(dplyr)

library(stats)
library(dplyr)
View(Telco_cleandata)
mydata<- select(Telco_cleandata,c('tenure','MonthlyCharges','TotalCharges'))
```

```{r}
cor(mydata)
mean(cor(mydata))
```
These variables are highly correlated, and they are eligible for PCA. The average correlation is 0.7. 

```{r}
PCA<- princomp(mydata)
attributes(PCA)
PCA
summary(PCA)
plot(PCA, type="l")
biplot(PCA, scale=0)


```
PCA loadings:

```{r}
PCA$loadings
```

```{r}
PC <- PCA$scores
View(PC)
```

```{r}
cor(PC)
```

Values are less than 1. These variables are independent

